Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-13 arxiv/intro.tex
polish introduction

\begin{abstract}
	Hard parameter sharing is a widely used approach to learn jointly from multiple tasks in many applications, such as text classification. The idea is to use a shared feature space for all tasks, while each task also has a separate layer for making the prediction.
%	It becomes increasingly important to understand when they work well on typical data. For example, the performance of hard parameter sharing depends on dataset properties such as their sample sizes. Yet, rigorously formulating such intuition can be challenging.
	This paper studies a fundamental question to better understand this approach: How does hard parameter sharing work given multiple linear regression tasks?
	We consider the high-dimensional setting, where the sample size and feature dimension become increasingly large in a fixed ratio. We present tight generalization bounds for two canonical cases: (i) multiple tasks with the same feature covariates; (ii) two tasks with arbitrarily different sample size ratios and covariance matrices. We also demonstrate that these estimates for the empirical loss are incredibly accurate in moderate dimensions. Finally, our results provide new explanations for several intriguing phenomena. For example, increasing one task's sample size helps another task initially by reducing variance, but hurts eventually due to increasing bias. This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in text classification tasks.
\end{abstract}

@@

Hard parameter sharing (HPS) is a widely used approach to learn from multiple tasks and goes back to the seminal work of \citet{C97}.
It is generally applied by sharing the feature layers between all tasks while keeping an output layer for every task.
Recent work has revived interest in this classical approach through many applications \cite{MTDNN19,ZSSGM18}.
Hard parameter sharing offers two critical advantages:
(i) it reduces model parameters since all tasks use the same feature space;
(ii) it reduces the need for labeled data from each task while augmenting the entire training dataset.

Hard parameter sharing is often thought of as a mechanism for inducing inductive bias.
Since all tasks share the same feature space, by restricting the space's \FY{what is "space's"}, HPS acts as a regularizer and reduces overfitting \cite{KD12,WZR20}.
Another source of inductive bias comes from the tasks and depends on datasets' properties such as sample sizes and task covariances \cite{WZR20}.
Previous generalization theories have considered the case where all tasks' sample sizes are equal \cite{B00,MPR16}.
Using Rademacher complexity or VC-based techniques, the generalization error scales down as all tasks' sample sizes increase \cite{AZ05,M06}.
%For, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.

This paper presents a new generalization theory to understand the hard parameter sharing approach by studying its performance in the high-dimensional linear regression setting.
Linear regression is arguably one of the most fundamental problems in statistics and machine learning.
We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and feature dimension grow linearly at a fixed ratio.
This is motivated by many multi-task learning applications, where the amount of labeled data from each dataset is usually insufficient for learning a single task.
For example, this is the case if a dataset's sample size is only a small constant factor of the feature dimension \cite{socher2013recursive}.
The high-dimensional setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.

>>>>

% The idea is to use a shared feature space for all tasks, while each task also has a separate layer for making the prediction.
\begin{abstract}
	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that their generalization properties have not been established in many cases. This paper studies a fundamental question to better understand this approach: How does hard parameter sharing work given multiple linear regression tasks? We develop new techniques and establish a number of new results in the high-dimensional setting, where the sample size and feature dimension become increasingly large in a fixed ratio. First, we show a sharp bias-variance decomposition of hard parameter sharing, given multiple tasks with the same features. Second, we characterize the asymptotic bias-variance limit for two tasks, even when they have arbitrarily different sample size ratios and covariate shifts. We also demonstrate that these limiting estimates for the empirical loss are incredibly accurate in moderate dimensions. Finally, we explain an intriguing phenomenon where increasing one task's sample size helps another task initially by reducing variance but hurts eventually due to increasing bias. This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in text classification tasks.
\end{abstract}

@@

Hard parameter sharing (HPS) for multi-task learning is widely used in empirical research and goes back to the seminal work of \citet{C97}.
Recent work has revived interest in this approach because it improves performance and reduces the cost of collecting labeled data \cite{MTDNN19,ZSSGM18}.
It is generally applied by sharing the feature layers between all tasks while keeping an output layer for every task.
Often, hard parameter sharing offers two critical advantages if successfully applied.
(i) It reduces model parameters since all tasks use the same feature space.
(ii) It reduces the amount of labeled data needed from each task by augmenting the entire training dataset.

Hard parameter sharing offers great intuitive appeal as an inductive transfer mechanism.
It reduces overfitting by acting as a regularizer \cite{R17}.
For example, by restricting the shared space's size, HPS encourages information sharing among multiple tasks \cite{KD12}.
Another source of inductive bias comes from the tasks and depends on datasets' properties such as sample sizes and task covariances \cite{WZR20}.
However, how these dataset properties impacts HPS has not been established.
%It becomes increasingly important to understand HPS' formal generalization properties.
Part of the challenge may be that HPS' generalization performance depends intricately on the sample size ratios and covariate shifts between tasks, not amenable to standard concentration results.
Previous results based on Rademacher complexity or VC dimensions have considered when all tasks' sample sizes are equal to logarithm factors of feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
%For, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.

This paper presents new techniques to study hard parameter sharing and establish a number of new results.
We consider regression analysis, which is arguably one of the most fundamental problems in statistics and machine learning.
We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and feature dimension grow linearly at a fixed ratio.
This is motivated by many multi-task learning applications, where the amount of labeled data from each dataset is usually insufficient for learning a single task.
For example, this is the case if a dataset's sample size is only a small constant factor of the feature dimension.
The high-dimensional setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.
